---
title: "ANLT-203_01 Assignment 4: K-means Clustering and Radial Basis Functions (RBF) "
author:  "Matthew Swogger - Ali Taheri"
date: "Mar 28, 2018"
output:
  html_document:
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stats)
library(flexclust)
library(MASS)
```


## Problem 1

### 1) RBF with gamma equal 5

```{r 1-1, warning=FALSE}

#Reading data to a dataframe
df=read.csv("vizData.csv",header=TRUE)

tmp.matrix = matrix(rep(df$x,nrow(df)) , nrow=nrow(df))
y=as.matrix(df$y)

gamma = 5

#Finding matrix of phi
phi = (exp(1))^(-gamma*((tmp.matrix-t(tmp.matrix))^2))
W=solve(phi) %*% y


X.vector = seq(-10,10,.01)
Y.vector =sapply(X.vector , function(new.point) (exp(1))^(-gamma*((df$x-new.point)^2)) %*% W )
plot(X.vector , Y.vector ,pch=18,col="blue",xlim=c(-5,5),ylim=c(-.7,0.7),xlab='input value', ylab= 'Prediction' , main= 'RBF regression with big gamma')
points(df$x, df$y , pch=8 ,col="red" , cex=1.5)


```

### 2) RBF with gamma equal 1/5

```{r 1-2, warning=FALSE}
gamma = 1/5

#Finding matrix of phi
phi = (exp(1))^(-gamma*((tmp.matrix-t(tmp.matrix))^2))
W=solve(phi) %*% y


X.vector = seq(-10,10,.01)
Y.vector =sapply(X.vector , function(new.point) (exp(1))^(-gamma*((df$x-new.point)^2)) %*% W )
plot(X.vector , Y.vector ,pch=18,col="blue",xlim=c(-5,5),ylim=c(-.7,0.7),xlab='input value', ylab= 'Prediction' , main= 'RBF regression with small gamma')
points(df$x, df$y , pch=8 ,col="red" , cex=1.5)


```

### 3) Explaination

It shows that only near neighbors will contribute more when gamma is big but curve would be more smooth when gamma is small and it shows that far points will contribute too.


## Problem 2

### 1) A function for K-Means clustring

```{r 2-1 , warning=FALSE}

#Function for K-Means clustring

my.KMeans <- function(df,num,k) { # k is number of clusters and num is number of features

#A list of list for saving clusters and centroids
result =vector('list',2) 

#number of iterations
n=1

#distance between centers of consecutive iterations
difference=1
 
#first random selection of k centroids
old.centroids = df[sample(nrow(df),k),1:num]

 
 while ((n <= 1000) & (difference >= 0.001)) {
   
  distances = dist2(as.matrix(df)[,1:num], old.centroids, method = "euclid") 
  #distances is data size x centroid size => 150 x 3
  #col 1 (150x1) is the distance between first centroid and all 150 points in dataset
  #col 2 (150x1) is the distance between second centroid and all 150 points in dataset
  #col 3 (150x1) is the distance between third centroid and all 150 points in dataset 
  
  
  #Selection of cluster for each point based on minimum distance to 3 centroids
  clusters = apply(distances, MARGIN = 1, which.min)
  
  #Finding new centroids by averaing x1 and x2 for all points of each cluster
  new.centroids = apply(as.matrix(df)[,1:num], MARGIN = 2, FUN = tapply, clusters, mean)
  
  #maximum distance between centers of two consecutive iterations
  difference = max(diag(dist2(old.centroids, new.centroids, method = "euclid")))
  
  old.centroids = new.centroids
  
  #updating number of iterations
  n=n+1
 }

 #saving clusters and centroids in result
 result[[1]] = clusters
 result[[2]] = new.centroids
 return(result)
}
```

### 2) Applying our function to respective dataset

```{r 2-2 , warning=FALSE}

#Reading data to a dataframe
df=read.csv("kMeansData.csv",header=TRUE)

final = my.KMeans(df,num=2,k=3)
clusters =final[[1]]
centroids = final[[2]]

#plotting points
plot(df[clusters == 1,1] , df[clusters == 1,2] ,pch=18,col="blue",xlim=c(0,8),ylim=c(0,3),xlab='x1', ylab= 'x2' , main= 'K-Means Clustring')
points(df[clusters == 2,1] , df[clusters == 2,2] , pch=18 ,col="red")
points(df[clusters == 3,1] , df[clusters == 3,2] , pch=18 ,col="black")
points(centroids[,1],centroids[,2], pch=8 ,col="green" ,cex=1.5)

```


##  Problem 3

### 1) K-Means clustring 
```{r 3-1 , warning=FALSE}

#Reading data to a dataframe
df=read.csv("rbfClassification.csv",header=TRUE)

final = my.KMeans(df,num=2,k=2)
clusters =final[[1]]
centroids = final[[2]]

print(centroids)


#plotting points
plot(df[clusters == 1,1] , df[clusters == 1,2] ,pch=18,col="blue",xlim=c(-3,3),ylim=c(-3,3),xlab='x1', ylab= 'x2' , main= 'K-Means Clustring')
points(df[clusters == 2,1] , df[clusters == 2,2] , pch=18 ,col="red")
points(centroids[,1],centroids[,2], pch=12 ,col="green" )  
```

### 2) RBF classification

```{r 3-2 , warning=FALSE}
#extraction of data points as classes in separate matrices
X=as.matrix(df[,1:2])  #data point
class=as.matrix(df$cls) #classes
class[class == 0] = -1  #Changing value of 0 one's to -1

dist.to.centroids = dist2(X, centroids, method = "euclid")
  #distances is data size x centroid size => 20 x 2
  #col 1 (20x1) is the distance between first centroid and all 20 points in dataset
  #col 2 (20x1) is the distance between second centroid and all 20 points in dataset

#function for finding accuracy
rbf.accuracy <- function (gamma) {

#Finding matrix of phi
tmp = (exp(1))^(-gamma*(dist.to.centroids)^2)
one.matrix=matrix(rep(1,nrow(df)),nrow=nrow(df))
phi=cbind(one.matrix,tmp)

#learned weights
W=ginv(phi) %*% class 

#prediction of classes by learned w's
predClass = sign(phi %*% W)

class[class == -1] = 0  #Changing value of -1 one's to 0
predClass[predClass == -1] = 0  #Changing value of -1 one's to 0

return(round(100 * sum(class == predClass) /nrow(df) ,2))
}

cat("Accuracy rate of RBF  parametric classification with gamms of 0.5 is",rbf.accuracy(0.5),"%\n\n")

#finding a value of gamma with maximim accuracy rate
gamma.vector = seq(0.001,1,.0005)
accuracy.vector =sapply(gamma.vector , function(gamma) rbf.accuracy(gamma) )
max.accuracy= max(accuracy.vector)
gamma.with.max.accuracy = gamma.vector[which.max(accuracy.vector)]
cat("Accuracy rate of RBF  parametric classification would be maximum with value of",max(accuracy.vector),"% at gamma of",gamma.vector[which.max(accuracy.vector)],"\n\n")
plot(gamma.vector , accuracy.vector ,pch=20,col="blue",xlim=c(0,.8),ylim=c(0,100),xlab='gamma', ylab= 'Accuracy Rate' , main= 'Accuracy of RBF classification based on gamma')


```

